Additional analysis

### 2019-03-13 README.Rmd
Update abstract and title

Title <- "The effect of NGO crackdowns on individual philanthropy"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2019"
```

@@

State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding, has become increasingly common. How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making? With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in many developing countries, many NGOs rely on funds from private donors in Western countries. Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO. We find that private donors are responsive to the legal difficulties international NGOs face abroad and are more likely to donate to legally besieged privately funded human rights NGOs. Additionally, already-likely donors give substantially more to legally restricted NGOs working on humanitarian issues. We conclude by discussing the implications for the sustainability of NGOs working abroad.

>>>>

Title <- "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2019"
```

@@

State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding and advocacy, has become increasingly pervasive across the globe. How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making? With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in various developing countries, many NGOs rely on funds from private donors in Western countries. Existing research has predominantly focused on individual-level determinants of philanthropy. However, we argue that domestic political environments of NGO host countries can also influence preferences of foreign private donors, and that crackdown on NGOs serve as a heuristic to donors of organizational deservingness. Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO. We find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad. We conclude by discussing the implications of our results on the sustainability of civil society organizations working in repressive countries.
